Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-02-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@

@@

%Transit information
%Full sample statistics
\subsection{Kepler and TESS photometry}
Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region. Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence. 
% 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html

\subsection{Stellar magnetic fields}
\cite{foster2022identifying} and \cite{reiners2022magnetism}

The intrinsic scatter in Eq. 4 in \cite{reiners2022magnetism} dominates the uncertainty in B over the uncertainty in stellar radius and $L_X$. We use the $+/-1\sigma$ values for the latter two for the final uncertainty estimate $\sigma B$

The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
\subsection{Transit mid-times}

The main data for this analysis are flare times. To obtain them, we gather the Kepler and TESS light curves for all star-planet systems, remove rotational variability trends, search the de-trended light curves for flares, and convert the flare times to orbital phases. We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal. We compare these results to theoretical SPI power $P_{SPI}$ using the scaling relations in~\cite{lanza2012starplanet}, where $P_{SPI}$ is proportional to

\begin{equation}
    P_{SPI} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2.
\end{equation}

$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_p$ is the planetary radius.

Orbital phase finding. Check coherence times. Orbital period is enough.
Use transit mid-times from the same mission if possible.

Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.

\cite{foster2022identifying} and \cite{reiners2022magnetism} to get Lx and then B.

@@

\subsubsection{DS Tuc A}
It's a multiple
\subsubsection{Kepler-1651}
It's a multiple

\subsubsection{Excluded flaring star-planet systems}
\paragraph{LTT 1445}
 LTT 1445 is a hierarchical triple wherein LTT 1445 A hosts two close-in planets, and LTT 1445 B and C are a tight binary system separated by about 7 arcsec, that is, blended in one TESS pixel~\citep{winters2019three}. Both the binary and LTT 1445 A have been detected with flares in X-ray~\citep{brown2022xray}. Recently, LTT 1445 A was found to host a second planet LTT 1445 Ac inwards of LTT 1445 Ab~\citep{lavie2022planetary}. The rotation periods are not known, so it does not appear in the final figure.

\paragraph{HD 41004 B}
Hierarchical system, composed of HD 41004 A and its Jupiter HD 41004 Ab, and HD 41004 B. an M dwarf, and its brown dwarf companion HD 41004 Bb. The rotation periods are not well-known, so it does not appear at all in the final figure.

@@

\bibliography{bib}

>>>>

\subsection{Kepler and TESS photometry}
Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region. Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence. 
% 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html

@@

%Transit information
%Full sample statistics

The main data for this analysis are flare times. To obtain them, we gather the Kepler and TESS light curves for all star-planet systems, remove rotational variability trends, search the de-trended light curves for flares, and convert the flare times to orbital phases. We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal. We compare these results to theoretical SPI power $P_{SPI}$

Orbital phase finding. Check coherence times. Orbital period is enough.
Use transit mid-times from the same mission if possible.
\subsection{Custom Anderson-Darlin test}
Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.

@@

\subsection{Stellar magnetic fields}
We derive B from Ro using Eq. XXX in \cite{reiners2022magnetism}:

The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
\subsection{Power of star-planet interaction}

We estimate the power of star-planet interaction generated by the strech-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn. 45), where $P_{sb}$ is proportional to

\begin{equation}
    P_{sb} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2 a^{-4} R_*^4.
\end{equation}

$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively; and $a$ is the semi-major axis.

We also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to

\begin{equation}
    P_{sb0} \sim B^2 v_{rel}  R_p^2  a^{-4} R_*^4
\end{equation}

For comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\cite{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \cite{kavanagh2022radio} to give

\begin{equation}
    P_{aw} \sim R_{p}^2  B_p^{2/3}  B^{1/3}  v_{rel}^2 * a^{-2}  
\end{equation}
where we approximate the stellar wind density $\rho_W$ with $a^{-2}$ and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B a^{-3}$, which result in the total $a^{-2}$ factor.

Here, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to

\begin{equation}
    P_{aw0} \sim R_p^2  B  v_{rel}^2  a^{-4}
\end{equation}

@@

@@

\subsection{Eccentricity}
The star-planet systems in this work do not have notably eccentric orbits.
\bibliography{bib}
